D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-07 ootavacuous.tex
Move acknowledgments and get todo list electronic
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

We are grateful to David Goldblatt, Jade Alglave, and Alan Stern for their
careful review of an early draft of this paper and to John Wickerson for
asking Paul for a rant and taking the proffered rant seriously.
We also owe David Goldblatt a debt of gratitude for his having asked an
insightful question at the right time, and for his ``Deathstation 9000''
demonic CPU.
Nonetheless, all errors and omissions in this paper are the sole property
of the authors.

% To do:
% Luc Maranget: Memory models.
% Richard Gristenthwaite: ARM hardware.
% Mark Rutland: ARM memory ordering.
% Will Deacon: ARM hardware, C++, and OOTA.
% Greg Kroah-Hartman and Linus Torvalds: FYI, trouble being caused.
% Christoph Hellwig: Why slow on BPF memory model.
% Miguel Ojeda: LKMM and Rust.
% Alice Ryhl: LKMM and Rust.
% Ralf Jung: Rust.
% Catalin Marinas: ARM and formal methods (qspinlock).
% Segher Boessenkool:  GCC.
% Dan Lustig: NVIDIA memory ordering.
% Andrea Parri: Memory models, RISC-V hardware.
% Jonas Oberhauser: Memory models.
% Hernan Ponce de Leon: Memory models.
% Palmer Dabbelt: RISC-V hardware.
% Ali Sezgin: P0422R0.
% Tony Tye: P0422R0.
% Other memory-model maintainers, including Peter Zijlstra.
% Derek Williams: PowerPC hardware.
% Hans Boehm: Skeptic, memory models, OOTA.  Suggestions for others?
% Olivier Giroux: Skeptic, memory models, NVIDIA.
% Luke Geeson: Whatever...  Review.
% Ori Lahav: Prior OOTA.
% Viktor Vafeiadis:  Prior OOTA.
% Derek Dreyer: Prior OOTA.
% Brian Demsky: Prior OOTA.

@@

>>>>

@@

We are grateful to David Goldblatt, Jade Alglave, and Alan Stern for their
careful review of an early draft of this paper and to John Wickerson for
asking Paul for a rant and taking the proffered rant seriously.
We also owe David Goldblatt a debt of gratitude for his having asked an
insightful question at the right time, his insights on combinations of
OOTA and UB, and for his ``Deathstation 9000'' demonic CPU.
Alan Stern located many unclear statements and gaps in reasoning.
Martin Uecker contributed valuable insights on backwards-propagating UB.
Nonetheless, all errors and omissions in this paper are the sole property
of the authors.

% @@@ reviewer to do.
% Luc Maranget: Memory models.
% Richard Gristenthwaite: ARM hardware.
% Mark Rutland: ARM memory ordering.
% Will Deacon: ARM hardware, C++, and OOTA.
% Greg Kroah-Hartman and Linus Torvalds: FYI, trouble being caused.
% Christoph Hellwig: Why slow on BPF memory model.
% Miguel Ojeda: LKMM and Rust.
% Alice Ryhl: LKMM and Rust.
% Ralf Jung: Rust.
% Catalin Marinas: ARM and formal methods (qspinlock).
% Segher Boessenkool:  GCC.
% Dan Lustig: NVIDIA memory ordering.
% Andrea Parri: Memory models, RISC-V hardware.
% Jonas Oberhauser: Memory models.
% Hernan Ponce de Leon: Memory models.
% Palmer Dabbelt: RISC-V hardware.
% Ali Sezgin: P0422R0.
% Tony Tye: P0422R0.
% Other memory-model maintainers, including Peter Zijlstra.
% Derek Williams: PowerPC hardware.
% Hans Boehm: Skeptic, memory models, OOTA.  Suggestions for others?
% Olivier Giroux: Skeptic, memory models, NVIDIA.
% Luke Geeson: Whatever...  Review.
% Ori Lahav: Prior OOTA.
% Viktor Vafeiadis:  Prior OOTA.
% Derek Dreyer: Prior OOTA.
% Brian Demsky: Prior OOTA.

% @@@ TODO:
% Create nicer sdep-evaluation example based on cbmc.
% Add a "Tools" section to the real-world constraints section.
%	Note the inversion from compiler, and the ability to complain
%	when analysis cannot be carried out accurately.
% Update wording.
% Add more detail on blocking UB to "Aside on Undefined Behavior".

% Additional snark:
% "This work reduces the problem of OOTA analysis to that of sequential
%	program analysis.  If you expect better verification of concurrent
%	code than of sequential code, you are in an intellectual state
%	of sin."
5 "Forcing relaxed loads to be ordered before subsequent relaxed stores
%	is an expensive no-op."

% One-pager:
% Threats to validity:
% Speed of light might not always be finite.
% Zero-sized atoms might be discovered.
% It might be possible to propagate information > c.
% It might be possible to violate causality.
% ML hallucination might convince people that OOTA is OK.
